\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-12 paper/main.tex
challenges
pass on section 2.3

\usepackage{multirow}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
  lots of activity recently but these numbers remain the same.}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
  \\ \bottomrule
\end{tabular}
\end{table}

@@

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Some GPU-related bug instances can only be reproduced with
specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
programming GPUs. These instances require specific CUDA drivers to be
installed on the system. Python virtual enviroments are not designed
to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers for the bug instances that require changes in
drivers.

@@

% \Fix{Abid, explain the steps you followed to create a bug
%   isntance. For example, (1) selected an issues (according to the
%   criteria defined in 2.1), (2) ...}

In order to add a bug to the dataset, a series of steps are followed.

\begin{itemize}
  \item A suitable issue is selected following the criteria defined in \ref{sec:selection-criterion}.
  \item A list of dependencies to reproduced the bug are written on a requirements text (requirements.txt).
  \item A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, a Dockerfile is written that can create a docker container with the required CUDA-driver installed along with the requirements.txt file and the python script copied into it.
  \item A script is written that can create the virtual environment or the Docker container and execute the python test.
  \item All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{itemize}

>>>>

\usepackage{multirow}
\usepackage{xcolor}
\usepackage{xspace}
\usepackage{listings}
\usepackage{enumitem}
\lstset{
  basicstyle=\ttfamily,
  columns=fullflexible,
  frame=single,
  breaklines=true,
  postbreak=\mbox{\textcolor{red}{$\hookrightarrow$}\space},
}
%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    Bib\TeX}}}

@@

\begin{table}
  \centering
  \caption{\label{table:bug-characterization}Characterization of
    reproducible bugs from \tname.\Fix{Is this up to date? I have seen
  lots of activity recently but these numbers remain the
  same.}\Fix{Can we add info about whether Python and/or C code causes
      the bug?}\Fix{Can we add info on whether it is GPU related
      (i.e., only manifests in GPUs)?}}
\begin{tabular}{l|rrr}
  \toprule & \multirow{2}{*}{\#} & \multicolumn{1}{r}{build} &
  \multicolumn{1}{r}{enviroment} \\ & & release-nightly & venv-docker
  \\ \cmidrule(lr){2-4} \jax{} & 44 & 43-1 & 43-1 \\ \torch{} & 33 &
  15-18 & 19-14 \\ \tf{} & 25 & 24-1 & 25-0 \\ \midrule
  \multicolumn{1}{c|}{$\Sigma$} & \numbugs{} & 82-20 & 87-15
  \\ \bottomrule
\end{tabular}
\end{table}

@@

\textbf{Handling bugs in specific GPU-CUDA versions requires OS
  changes:} Some GPU-related bug instances can only be reproduced with
specific versions of CUDA~\cite{cuda}, NVIDIA's platform and API for
programming GPUs. These instances require specific CUDA drivers to be
installed on the system. Python virtual enviroments are not designed
to enable change of OS drivers.
% GPU builds\Fix{I don't understance GPU builds. do you mean
%   GPU vendor/version? give example} and specific CUDA builds. 
% Changing different virtual environments does not change the CUDA
% versions\Fix{Do you mean ``it is not possible to change the CUDA (or
%   GPU) version with Python's virtual environments''?} of the
% system. 
% That is why we use Docker when a bug relies on a specific
% version of CUDA to be installed in the system.
We use Docker containers~\cite{merkel2014docker} for the bug instances
that require changes in drivers.

@@

The following steps show the method we use to create bug instances:

\begin{enumerate}[leftmargin=0.5cm]
  \item Select an issue following the criteria defined in Section~\ref{sec:selection-criterion};
  \item Write file \CodeIn{requirements.txt} with the list of dependencies to reproduce the bug;
  \item Create a file showing the code that causes the bug (for documentation);
  \item Create a file with a \CodeIn{pytest} test case that passes if
    the code triggers the buggy behavior documented in the issue;
    %% A python file is created that contains the bug revealing code, along with a test (pytest) that passes upon successfully trigerring the buggy behavior.
  \item If the bug depends on a CUDA-specific build, write a
    Dockerfile to create a container including the needed CUDA-driver
    and the other artifacts mentioned above (e.g., test file and
    requirements);
    %% along with the requirements.txt file and the python
    %% script copied into it.
  \item Write a script that creates the virtual environment (either
    Python's \CodeIn{venv}~\cite{venv} or Docker container) and runs
    the test on it;
  \item Create a directory \CodeIn{<lib>/<bug-id>} containing all the
    artifacts mentioned above, where \CodeIn{lib} refers to the
    affected library and \CodeIn{bug-id} is a fresh identifier of the
    bug instance.
    %% All files are put into a single self-contained folder with the issue id in the name so that the tools exposed by the framework of our tool can find and execute the the bug reproduction script.
\end{enumerate}
